Carbon bias

### 2015-10-22 Rmd/carbon-bias.Rmd
22/10/2015 revision. Revisions through results. See changelog.

# yl <- range(cb_statsw_mu[, LC, with = FALSE], 
#             cb_statsw_mua[, LC, with = FALSE])
# yl <- round(yl / 10) * 10
yl <- c(-290, 290)
yax <- seq(yl[1], yl[2], 20)
xax <- seq(1, 6, 5 / (length(yax) - 1))

>>>>

# yl <- range(cb_statsw_mu[, LC, with = FALSE], 
#             cb_statsw_mua[, LC, with = FALSE])
# yl <- round(yl / 10) * 10
yl <- c(-150, 150)
yax <- seq(yl[1], yl[2], 10)
xax <- seq(1, 6, 5 / (length(yax) - 1))
